Deep Reinforcement Learning for Conservation Decisions

### 2022-05-31 manuscript/manuscript.Rmd
Validation paragraph first go

We do recognize the need for more complex, "precise" models to derive quantitatively precise management policy in specific management problems such as fisheries, forestry, or climate change mitigation efforts. 
The examples here should provide ecologists with a greater background to engage in the collaborative development of such methods, while also highlighting challenges which ecological problems pose to existing techniques.
Even the simple models we consider here contain sources of complexity such as hysteresis that are likely commonplace to ecological problems but have not been well represented in RL research to date. 
Applying RL to a range of "precise" models is currently beyond the scope of any one paper: it will require not only more computational resources but more collaborations between large teams of ecologists and computer scientists.

>>>>

This paper does not intend to validate deep RL as a method that should be used to directly inform decision-making on current conservation problems.
Instead, we have selected example problems to provide ecologists with a greater background to engage in the collaborative development of deep RL-based methods, while also highlighting challenges which ecological problems pose to existing techniques.
Validating deep RL for current conservation problems is beyond the scope of any one paper: this will necessitate examining a range of more "precise" models which will require more computational resources than is available to most researchers and extensive collaboration between large teams of ecologists and computer scientists.
